
\cvsection{Achievements}
\begin{itemize}
\item Winner at Social Innovation Hackathon "Accelathon 2019" conducted by BCIC (Bangalore Chambers of Industry and Commerce)
\item Won 3rd Consolation prize at Quest Global IoT Hackathon.
\end{itemize}

\cvsection{Honors \& Awards}
\begin{itemize}
    \item Presented a paper on "Safe Ride: Automatic Detection of Potholes and Humps on Roads using ultrasonic sensor" in Iternational Conference on Innovation Research in Engineering, Management and Sciences ( ICIREMS-2019 ).
    \item Recipent of Intel Edge AI Scholarship a Nano degree course at Udacity.
\end{itemize}

% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} https://www.overleaf.com/project/5e2d2ae2fc35cd000142a1cc
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Projects}
\cvproject{Safe Ride}
\begin{itemize}
\item An IoT based framework created utilizing Rasberry Pi which catches the geographic co-ordinates of the Potholes and Humps utilizing a GPS recipient. Voice notice is given to the driver inside a given range by monitoring his GPS area by utilizing the android application\%.
\end{itemize}

\cvproject{Mancala}
\begin{itemize}
\item An Android Gaming Application in which two-player turn-based technique table games played with little stones set in columns of gaps.
\end{itemize}

\cvproject{Smart Stick}
\begin{itemize}
\item An IoT model where Blind individuals can stroll with a smart stick which can recognize the obstacles en route by a buzzing sound and send the location of the individual to the parent or guardian utilizing google map API. 
\end{itemize}

\cvproject{Real Time Stock Data Analysis}
\begin{itemize}
\item A prototype of an Application which functions with implementing the use of Markov chains to predicting stock prices.
\end{itemize}

\cvproject{Digital Registration Form Application}
\begin{itemize}
\item It is utilized for lodging Entries of leaves and attendance which would assist us with lessening the utilization of paper.
\end{itemize}

\cvproject{Spam classification using Neural Net}
\begin{itemize}
\item A C++ Object-oriented Application that gives a gave brief outline about the spamming classification in neural net for client id and username. 
\end{itemize}

\cvproject{Battery Monitor}
\begin{itemize}
    \item It is an IoT project which uses Arduino board and IR to detect the battery charging when it is fully charged it can switch the power supply.
\end{itemize}

\cvproject{Digital Library}
\begin{itemize}
    \item it has two mode admin and librarian login where books can be added, removed, Borrowed, returned and Viewed.
\end{itemize}
